Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-02-05 README.Rmd
Added Bob's ORCID
getting travis up and running again

# robinson2020
[![Travis-CI Build Status](https://travis-ci.org/bocinsky/robinson2020.svg?branch=master)](https://travis-ci.org/bocinsky/robinson2020)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio)

@@

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428), Jacob Freeman, Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), Robert L. Kelly, (2020). _`r Title`_. Under review.

@@

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. Binder uses (rocker-project.org)[rocker-project.org Docker] images to ensure a consistent and reproducible computational environment. These Docker images can also be used locally.

@@

>>>>

# robinson2020
[![Travis build status](https://travis-ci.org/people3k/robinson2020.svg?branch=master)](https://travis-ci.org/people3k/robinson2020)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/people3k/robinson2020/master?urlpath=rstudio)

@@

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428), Jacob Freeman, Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), Robert L. Kelly[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9737-0152), (2020). _`r Title`_. Under review.

@@

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/people3k/robinson2020/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. Binder uses (rocker-project.org)[rocker-project.org Docker] images to ensure a consistent and reproducible computational environment. These Docker images can also be used locally.

@@

Or, simply install straight from Github:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("people3k/robinson2020")
```
